Sensor Clusterization in D-optimal Design in Infinite Dimensional Bayesian Linear Inverse Problems

### 2024-09-09 revision/rev3.tex
Restred

\AR These are two great points. Indeed, the growth of eigenvalues of
the Laplacian is different in higher dimensions. This is why in higher
dimensions we would have to take as prior \(u_0 \sim
\mathcal{N}(\param_0, (-\Delta)^{-\gamma})\), for some \(\gamma >
d/2\) in order to maintain regularity of prior realizations. I decided
not to include a discussion on the choice of priors in higher spatial
dimensions because (1) it would require too much exposition and make
me digress from the main points I wanted to convey and (2) due to
technical difficulties in installing packages for inverse problems
\cite{attia2023pyoed, villa2021} I had to implement the inverse
problem of the 1D heat equation from scratch, so I decided to leave
out experiments in higher dimensions.

@@

\AR the Mat\'ern-like prior actually arises by using a Laplacian-like
operator as a prior \cite{rue2011}. So a study of this example (with
and without correlated errors) is already included in the paper. I am
afraid implementing another inverse problem is out of scope for the
present paper since I was not able to install common packages for
inverse problems \cite{attia2023pyoed, villa2021} on my machine.

>>>>

\AR These are two great points. Indeed, the growth of eigenvalues of
the Laplacian is different in higher dimensions. This is why in higher
dimensions we would have to take as prior \(u_0 \sim
\mathcal{N}(\param_0, (-\Delta)^{-\gamma})\), for some \(\gamma >
d/2\) in order to maintain regularity of prior realizations. I decided
not to include a discussion on the choice of priors in higher spatial
dimensions because (1) it would require too much exposition and make
me digress from the main points I wanted to convey and (2) due to
technical difficulties in installing packages for inverse problems
\cite{attia2023pyoed, villa18} I had to implement the inverse problem
of the 1D heat equation from scratch, so I decided to leave out
experiments in higher dimensions.

@@

\AR the Mat\'ern-like prior actually arises by using a Laplacian-like
operator as a prior \cite{rue2011}. So a study of this example (with
and without correlated errors) is already included in the paper. I am
afraid implementing another inverse problem is out of scope for the
present paper since I was not able to install common packages for
inverse problems \cite{attia2023pyoed, villa18} on my machine.
